Decentralisation of Poverty - Replication Analysis

### 2016-08-05 markdown/draft.RmD
update markdown doc - update date; add tables direct from values

---
title: "Decentralisation of Poverty - Replication Analysis"
author: "Jon Minton"
date: "4 August 2016"
output: html_document
---

@@

```{r show_map, eval = TRUE, echo = FALSE, cache = FALSE, message = FALSE, warning = FALSE}
dz_2011 %>%
 append_data(., centre_distance, key.shp = "DataZone", key.data = "datazone", ignore.duplicates = T) %>%
 tm_shape(.) +
 tm_polygons(col = "nearest_centre", border.alpha = 0) -> map_nearest_centre

@@

For Glasgow, the RCI scores (with 95% credible intervals, CrIs) for 2004 and 2012, and for the difference between these two periods, are as follows:

Quantile   | RCI, 2004 | RCI, 2012  | Change  
---------- | --------  | ---------- | -------  
median     | 0.144     | 0.093      | -0.051
2.5% CrI   | 0.142     | 0.091      | -0.054
97.5% CrI  | 0.146     | 0.096      | -0.047

From this we can conclude that there has been a statistically significant fall in RCI over these two periods using the SIMD income deprivation measure, as there had been for out-of-work benefits-based measures for 2001 and 2011 in Kavanagh at al 2016.

As with Kavanagh et al 2016 Dissimilarity index scores (D) were also calculated for both periods, along with change between them. These are shown in the table below, and also show statistically significant falls.

Quantile   | D, 2004 | D, 2012  | Change  
---------- | ------- | -------- | ------- 
median     | 0.368   | 0.315    | -0.053
2.5% CrI   | 0.366   | 0.313    | -0.056
97.5% CrI  | 0.370   | 0.317    | -0.051

#### Dundee

Quantile   | RCI, 2004 | RCI, 2012  | Change  
---------- | --------  | ---------- | -------  
median     | 0.304     | 0.256      | -0.048
2.5% CrI   | 0.298     | 0.251      | -0.056
97.5% CrI  | 0.309     | 0.262      | -0.040

Quantile   | D, 2004 | D, 2012  | Change  
---------- | ------- | -------- | ------- 
median     | 0.414   | 0.377    | -0.037
2.5% CrI   | 0.409   | 0.372    | -0.044
97.5% CrI  | 0.418   | 0.382    | -0.030

#### Aberdeen

Quantile   | RCI, 2004 | RCI, 2012  | Change  
---------- | --------  | ---------- | -------  
median     | 0.218     | 0.187      | -0.031
2.5% CrI   | 0.213     | 0.181      | -0.040
97.5% CrI  | 0.224     | 0.193      | -0.022

Quantile   | D, 2004 | D, 2012  | Change  
---------- | ------- | -------- | ------- 
median     | 0.385   | 0.360    | -0.024
2.5% CrI   | 0.379   | 0.355    | -0.032
97.5% CrI  | 0.390   | 0.366    | -0.017

#### Edinburgh

Quantile   | RCI, 2004 | RCI, 2012  | Change  
---------- | --------  | ---------- | -------  
median     | 0.013     | -0.013     | -0.025
2.5% CrI   | 0.009     | -0.016     | -0.030
97.5% CrI  | 0.016     | -0.009     | -0.020

Quantile   | D, 2004 | D, 2012  | Change  
---------- | ------- | -------- | ------- 
median     | 0.385   | 0.319    | -0.067
2.5% CrI   | 0.382   | 0.316    | -0.071
97.5% CrI  | 0.389   | 0.322    | -0.062

>>>>

---
title: "Decentralisation of Poverty - Replication Analysis"
author: "Jon Minton"
date: "5 August 2016"
output: html_document
---

@@

```{r show_map, eval = TRUE, echo = FALSE, cache = FALSE, message = FALSE, warning = FALSE}

dz_2011 %>%
 append_data(., centre_distance, key.shp = "DataZone", key.data = "datazone", ignore.duplicates = T) %>%
 tm_shape(.) +
 tm_polygons(col = "nearest_centre", border.alpha = 0) -> map_nearest_centre

@@

### RCI, Aberdeen

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Aberdeen", measure == "RCI") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "RCI, Aberdeen")

### RCI, Dundee

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Dundee", measure == "RCI") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "RCI, Dundee")

### RCI, Edinburgh

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Edinburgh", measure == "RCI") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "RCI, Edinburgh")

### RCI, Glasgow

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Glasgow", measure == "RCI") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "RCI, Glasgow")

## Dissimilarity calculations

This section will present the results of the Dissimilarity index calculations, using the Bayesian modelling approach used in Kavanagh et al 2016.

### D, Aberdeen

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Aberdeen", measure == "D") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "D, Aberdeen")

### D, Dundee

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Dundee", measure == "D") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "D, Dundee")

### D, Edinburgh

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Edinburgh", measure == "D") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "D, Edinburgh")

### RCI, Glasgow

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Glasgow", measure == "D") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "D, Glasgow")
